Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2022-08-04 vertical-thermal-review.Rmd
progress on editorial requests
a few updates

Martijn Slot^3^

Ian R. McGregor^4^ (Orcid ID: 0000-0002-5763-021X)

Elsa M. Ordway^2,5^

@@

Thomas N. Buckley^8^

Kristina J. Anderson-Teixeira^1,3^* ( Orcid ID : 0000-0001-8461-9713)

@@

3. Forest Global Earth Observatory, Smithsonian Tropical Research Institute, Apartado Postal 0843-03092, Panama City, Panama

@@

## Acknowledgements
Thanks to Valentine Herrmann, Norbert Kunert, Camille Piponiot, Peter B. Boucher and Andrew B. Davies for providing figure materials. 
This manuscript benefited from feedback from Eleinis Ávila-Lovera, the ForestGEO Ecosystems & Climate lab at NZCBI, and two anonymous reviewers.
Funding was provided by the Smithsonian Institution.

>>>>

Martijn Slot^3^ (ORCID: 0000-0002-5558-1792; Twitter: @martijn_slot; Facebook: martijn.slot.52)

Ian R. McGregor^4^ (ORCID: 0000-0002-5763-021X; Twitter: @ecoterrestrian)

Elsa M. Ordway^2,5^ (ORCID: 0000-0002-7720-1754; Twitter: @ElsaOrdway)

@@

Thomas N. Buckley^8^ (ORCID: 0000-0001-7610-7136; Twitter: @TomBuckleyLab)

Kristina J. Anderson-Teixeira^1,3^* (Orcid ID : 0000-0001-8461-9713; Twitter: @K_A_Teixeira)

@@

3. Smithsonian Tropical Research Institute, Apartado Postal 0843-03092, Panama City, Panama

@@

## Acknowledgements
Thanks to Valentine Herrmann, Norbert Kunert, Camille Piponiot, Peter B. Boucher and Andrew B. Davies for providing figure materials. 
This manuscript benefited from feedback from Eleinis Ávila-Lovera, the ForestGEO Ecosystems & Climate lab at NZCBI, and two anonymous reviewers.
Funding was provided by the Smithsonian Institution, NSF grant #1951244 to LS and TNB, and USDA-NIFA Hatch project grant #1016439 to TNB.
